Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
eval scaling

One of the key parameters of the aggregator is the message
timeout. All messages that are queued must eventually be sent in order
to ensure progress. In the best case, we are able to aggregate enough
messages to fill an aggregation buffer and cause it to be sent, but as
we scale up, the average rate of messages heading to a common
destination decreases, and this gets harder. To bound the problem, the
aggregator includes a timeout. Any packet waiting this long must be sent.

Figure~\ref{fig:bfs-sweep-flushticks} shows a sweep of this parameter
for 32-node and 96-node BFS runs. The optimal timeout value varies
with the size of the job. In the 32-node job, performance peaks with a
2 ms timeout; with the 96-node job, performance peaks with a 14 ms
timeout.

@@

Figure~\ref{fig:bfs-sweep-workers} shows a sweep of the maximum number
of active tasks per core, holding all other parameters
constant. Again, the optimal value varies with the size of the
run. For 32 nodes, a maximum of 3072 active tasks per core gives the
best result; for 96 nodes, 16000 tasks is best.

@@

\TODO{(difference with BFS)}

>>>>

One of the key parameters of the aggregator is the message
timeout. All messages that are queued must eventually be sent in order
to ensure progress. In the best case, we are able to aggregate enough
messages to fill an aggregation buffer and cause it to be sent, but as
we scale up, the average rate of messages heading to a common
destination decreases, and this gets harder. To bound the problem, the
aggregator includes a timeout. Any packet waiting this long is sent
the next time the communications layer is serviced.

Figure~\ref{fig:bfs-sweep-flushticks} shows a sweep of this parameter
for UTS, BFS, and Betweenness Centrality on 16 nodes, using the
datasets described previously. The maximum number of workers is fixed
at 2048. All the benchmarks show a performance peak with a 2
millisecond timeout; at this point we are delaying long enough to
aggregate the largest packets we can; setting the parameter higher
causes tasks to wait longer for responses, but few new requests are
being generated.

@@

Figure~\ref{fig:bfs-sweep-workers} shows a sweep of the maximum number
of active tasks (workers) per core for each of our three benchmarks on
16 nodes. The aggregator timeout is set at 1 ms for UTS and 2 ms for
BFS and Betweenness Centrality. The performance peak shifts in this
case, with UTS peaking at 1536 workers, BFS peaking at 2048 workers,
and Betweenness Centrality peaking at 3072 workers. This is the point
where we have enough workers to cover the latency of aggreation. The
different values reflect the different amounts of work done by a task
in each benchmark; UTS does the least, while Betweenness Centrality does the most.

@@

%\TODO{(difference with BFS)}
